\documentclass{beamer}

\usetheme[progressbar=foot]{metropolis}
%\usepackage{appendixnumberbeamer}

%\usepackage{booktabs}
\usepackage[scale=2]{ccicons}

\usepackage{pgfplots}
\usepgfplotslibrary{dateplot}
\pgfplotsset{compat=1.17} 

\usepackage{xspace}
\usepackage{xcolor}
\usepackage{graphicx}
\usepackage{hyperref}
\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    urlcolor=cyan,
    citecolor=green
}


\setbeamertemplate{frame footer}{MGMT 675: Generative AI for Finance}

\title{MGMT 675: Generative AI for Finance}
\subtitle{FMA 2025}

\date{October 24, 2025}
\author{Kerry Back\\ 
Jones Graduate School of Business\\
Rice University}


\begin{document}

\maketitle


\begin{frame}{Overview}
    \begin{itemize}
    \item Half-semester MBA course at end of 1st year
    \item Course comes after: 
    \begin{itemize}
    \item Core finance (semester) 
    \item Excel-based Applied Finance (half-semester)
    \end{itemize}
    \item Finance topics mostly repeated from prior courses
    \item Ideas apply to courses of different lengths, at different points in the curriculum, and for different student groups
    \end{itemize}

\end{frame}

\begin{frame}{Learning Objectives}
\begin{enumerate}
    \item Working with AI
    \begin{enumerate}%\renewcommand{\labelenumii}{(\alph{enumii})}
        \item Collaborate with AI that uses Python to conduct financial analysis 
        \item Refine prompts to make effective use of AI 
    \end{enumerate}
    \item Corporate implementations of AI: system prompts, retrieval-augmented generation (RAG), and agents
    \item Build with AI 
    \begin{enumerate}
        \item Custom chatbots, apps, and AI-enabled apps for financial analysis
        \item AI agents (chatbots with tools)
    \end{enumerate}
\end{enumerate}
\end{frame}

\begin{frame}{CNBC on JPMorgan, 9/30/2025}

Derek Waldron, , Chief Analytics Officer:
\begin{itemize}
\item (What we're working towards is that) every employee will have their own personalized AI assistant; every process is powered by AI agents, and every client experience has an AI concierge.
\item You'll still have people at the top who are managing and have relationships with clients, but many, many of the processes underneath are now being done by AI systems.
\end{itemize}


Workers would shift from being creators of reports or software updates, or "makers" ... to "checkers" or managers of AI agents doing that work.

\end{frame}

\begin{frame}{Yeyati, Brookings, 2025}

\begin{itemize}
\item As AI models begin to handle underwriting, compliance, and asset allocation, the traditional architecture of financial work is undergoing a fundamental shift.
\item As job descriptions evolve, so does the definition of financial talent. Excel is no longer a differentiator. Python is fast becoming the new Excel. 
\item But technical skills alone will not cut it. The most in demand profiles today are those that speak both AI and finance.
\end{itemize}
\end{frame}

\begin{frame}{Website: \href{https://genai4finance.kerryback.com}{genai4finance.kerryback.com}}
\begin{itemize}
\item Course description aimed at instructors
\item Link to blog: short posts about teaching various topics on AI and finance 
\item Link to 2025 course syllabus \& slides
\item Link to 2026 course syllabus (slides coming soon)
\item Link to these slides
\item Link to slides for upcoming talk on Integrating AI into Finance Teaching
\item Link to Jupyter notebooks (and soon slides) for teaching Python to MBAs
\end{itemize}
\end{frame} 

\end{document}


